---
title: "Business Intelligence Lab Submission Markdown"
author: "<team kubwa>"
date: "<23/10/2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one Student name, class group (just the letter; A, B, or C), and ID per line, e.g., 123456 - A - John Leposo; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  128998 - B - Crispus Nzano                                                                                                                                            |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  134100 - B - Timothy Obosi                                                                                                                                             |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  134092 - B - Alison Kuria                                                                                                                                                                                                                                                 |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  135269 - B - Clifford Kipchumba                                                                                                                          |
|                                                   |                                                                                                                                                      |
|                                                   | 5.  112826 - B - Matu Ngatia                                                                                                                          |
|                                                   |                                                  
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Team Kubwa                                                                                                       |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## formatR - Required to format R code in the markdown ----

if (require("languageserver")) {
  require("languageserver")
} else {
  install.packages("languageserver", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

# Introduction ----
# Association rule learning helps to boost business by determining which items
# are bought together.

# A business that has this information can use it for promotional pricing or
# for product placement.

# Association rules are employed in many application areas including Web usage
# mining, intrusion detection, continuous production, bioinformatics, etc.

# In contrast with sequence mining, association rule learning typically does
# not consider the order of items either within a transaction or across
# transactions.

# Association rule learning -> association rule mining -> market basket analysis
# The primary difference lies in the context and purpose of the analysis.
# Association rule mining is a more general technique that can be applied in
# various domains, while
# Market Basket Analysis is a specialized application used in the retail
# industry to understand customer purchasing behavior.

# STEP 1. Install and Load the Required Packages ----
## arules ----
if (require("arules")) {
  require("arules")
} else {
  install.packages("arules", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## arulesViz ----
if (require("arulesViz")) {
  require("arulesViz")
} else {
  install.packages("arulesViz", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## tidyverse ----
if (require("tidyverse")) {
  require("tidyverse")
} else {
  install.packages("tidyverse", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## readxl ----
if (require("readxl")) {
  require("readxl")
} else {
  install.packages("readxl", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## knitr ----
if (require("knitr")) {
  require("knitr")
} else {
  install.packages("knitr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## ggplot2 ----
if (require("ggplot2")) {
  require("ggplot2")
} else {
  install.packages("ggplot2", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## lubridate ----
if (require("lubridate")) {
  require("lubridate")
} else {
  install.packages("lubridate", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## plyr ----
if (require("plyr")) {
  require("plyr")
} else {
  install.packages("plyr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## dplyr ----
if (require("dplyr")) {
  require("dplyr")
} else {
  install.packages("dplyr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## naniar ----
if (require("naniar")) {
  require("naniar")
} else {
  install.packages("naniar", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## RColorBrewer ----
if (require("RColorBrewer")) {
  require("RColorBrewer")
} else {
  install.packages("RColorBrewer", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}


```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console



## FORMAT 2: Basket Format----
# An example of the single format transaction data is presented

market_basket_format <-
  read.transactions("data/market_basket_transaction.csv",
                    format = "basket", sep = ",", cols = 2)
View(market_basket_transactions)
print(market_basket_transactions)

# We can read data from an Excel spreadsheet as follows:
retail <- read_excel("data/market_basket_transactions.csv")
dim(items)

### Handle missing values ----
# Are there missing values in the dataset?
any_na(items)

# How many?
n_miss(items)

# What is the proportion of missing data in the entire dataset?
prop_miss(items)

# What is the number and percentage of missing values grouped by
# each variable?
miss_var_summary(items)

# Which variables contain the most missing values?
gg_miss_var(items)

# Which combinations of variables are missing together?
gg_miss_upset(items)

#### OPTION 1: Remove the observations with missing values ----
items_removed_obs <- items %>% filter(complete.cases(.))



dim(items_removed_obs)

# Are there missing values in the dataset?
any_na(items_removed_obs)

# What is the number and percentage of missing values grouped by
# each variable?
miss_var_summary(items_removed_vars_obs)
dim(items_removed_vars_obs)

items_removed_vars_obs <- items_removed_vars_obs %>% filter(complete.cases(.))

tr <-
  read.transactions("data/market_basket_transactions.csv",
    format = "basket",
    header = TRUE,
    rm.duplicates = TRUE,
    sep = ","
  )

print(tr)
summary(tr)

itemFrequencyPlot(tr, topN = 10, type = "absolute",
                  col = brewer.pal(8, "Pastel2"),
                  main = "Absolute Item Frequency Plot",
                  horiz = TRUE,
                  mai = c(2, 2, 2, 2))

itemFrequencyPlot(tr, topN = 10, type = "relative",
                  col = brewer.pal(8, "Pastel2"),
                  main = "Relative Item Frequency Plot",
                  horiz = TRUE,
                  mai = c(2, 2, 2, 2))
                  
association_rules <- apriori(tr_stock_code,
                             parameter = list(support = 0.01,
                                              confidence = 0.8,
                                              maxlen = 10))


summary(association_rules)
inspect(association_rules)
# To view the top 10 rules
inspect(association_rules[1:10])
plot(association_rules)

subset_rules <-
  which(colSums(is.subset(association_rules,
                          association_rules)) > 1)
length(subset_rules)
association_rules_no_reps <- association_rules[-subset_rules]





**etc.** as per the lab submission requirements. Be neat and communicate in a clear and logical manner.








